I am excited to learn about your job opening because I have been searching for a
company just like yours to challenge my software engineer skills and improve my
strengths in a motivated and highly functional team. In reviewing my resume,
you will find that I possess all the attributes of a perfect match, from programming
competence in Python (Django, Flask), JavaScript (ReactJS, Redux, AngularJS, NodeJS, ExpressJS), SQL
(PostgreSQL, MySQL) and REST APIs. As proof of experience with Python and ReactJS,
I'm proud to show some personal projects in my Github where I practice and keep
me up-to-date (Python: \href{https://github.com/joaosr/geo}{geo}, \href{https://github.com/joaosr/somemes/tree/target}{somemes},
\href{https://github.com/joaosr/fake_hotel}{fake\_hotel}; ReactJS: \href{https://github.com/joaosr/buddenbrooks}{buddenbrooks}).

During my seven years of experience as a Full-stack Software Developer, I have
gained extensive knowledge of frontend as well as of backend architectures that
I developed through work experiences in proactive international teams and personal
studies. As a team player with a positive attitude and energy, I love to discuss
possible options with my colleagues as well as encourage the team to keep a high
software quality by doing code review, refactoring and pair programming. Along
with these practices, I acquired an excellent capability to analyze stakeholder's
needs and feedbacks, which allow me to bring refined insights and accurate estimation
to the workgroup efforts.

My acquired expertise affected not only my career but also had an impact on the
achievements of the companies that I have worked for. My current employer
\href{https://www.realxdata.com/}{Realxdata} has a solid reputation as a software
innovation startup in the German PropTech market, which supplies the real estate
industry with big data analysis. My previous employer, \href{http://terras.agr.br/}{Terras App Solutions},
is a company that affords geospatial applications for the Brazilian agribusiness
market and helps farmers track their productions and finances. In both cases,
I was one of the first employees in the firm, and I helped to build a robust,
competitive and prominent business from the beginning until maturation. As my
experiences illustrate, I am particularly well qualified for the position.
I thrive in an atmosphere of challenge, I am a quick learner, and I do not spare
any effort or time to find potential weak spots which will boost the gain of \companyName.

I believe that I can very comfortably meet your requirements as the ideal candidate
for this position and enthusiastically anticipate discussing your specific needs
and my ability to meet them in an interview. I look forward to introducing myself
personally to you, maybe in an opportunity in the comings weeks.
