\documentclass[a4paper]{joaosoares-letter}
\signature{João Soares}

\begin{document}
\longindentation=0pt

\begin{letter}{\bfseries Door2Door GmbH\\Torstraße 109\\10119 Berlin\\Germany}

\namesection{João}{Soares}{	Passagem Liberal 245, Belém, PA, Brazil \ \lpipe\ \ eng.jmsoares@gmail.com \ \lpipe\ \ + 55 91 98220-3284}

\date{Belém, \today}

\opening{Dear Mr. Barker,}{Position as a … on LinkedIn (10.02.107)}

	Your recent job posting on berlinstartupjobs.com caught my attention. Door2Door seems to be the company that I am looking for. Door2Door’s efforts to introduce shared, on-demand public transport and to offer this to its users with the help of maptools really impressed me. Helping to create a city with less co² emissions is a way of thinking for the future of cities. 

	My four years of experience as a software developer that I have in addition to my computer engineering degree, put me face to face with similar important problems such as the Amazon deforestation and its contributions to the growth in global co² emissions. During this time, I have been working on the development of eight software projects for web and mobile platforms in total which I programmed mainly in Javascript, Python and Java for Android. The mayor project I have been working on was the Deforestation Analyses Tool in cooperation with the Google Earth Engine team. In this experience I have programmed services for acquisition and image processing using the Flask python web framework and the google earth engine (GEE) python API. The maintenance of the web platform I programmed using the Backbone.js framework and JQuery plugins. My work experiences showed me the possibilities of visualizing the deforestation of the Amazon rainforest through the combination of algorithms and satellite images. This allows geospatial analists to extract information out of satellite images and edit them afterwards for their own use.

The above mentioned background examples take me looking for a job in a new country, and Berlin as an international city seems to be the perfect place. Working at Door2Door would be an ideal opportunity to expand my professional horizon as a passionate programmer and share a great valuated work culture with an international and outside of the box thinking team such as Door2Door’s team. 

\closing{Thank you for your consideration and looking forward to your reply,}
\vspace{20pt}
\ps

P.S. You can find the full text of GFDL license at
\vspace{\fill}
\encl{Resume}

\end{letter}
\end{document}
