\documentclass[a4paper]{joaosoares-letter}
\usepackage{ragged2e}
\signature{João Soares}

\begin{document}
\longindentation=0pt


\begin{letter}{\bfseries KAYAK Germany GmbH\\Straße der Pariser Kommune 8\\10243 Berlin\\Germany}

\namesection{João}{Soares}{	Passagem Liberal 245, Belém, PA, Brazil \ \lpipe\ \ eng.jmsoares@gmail.com \ \lpipe\ \ + 55 91 98220-3284}

\date{Belém, \today}


\opening{Dear Ms. Li,}{Full Stack Python Software Developer - Berlin, Germany on your web page (18.02.2017)}

as a member of the Brazilian Python community I am searching for a company just like yours to challenge my programming skills and improve my personal strengths in a motivated and highly functional team. In reviewing my resume, you will find that I possess all the attributes of a perfect match, from programming skills mainly in Python, Javascript and Java to frameworks like Django and Node.js.

During my four years of experience as a Full-stack Software Developer I have gained major experiences in developing four strong and stable web mapping tools such as \href{https://goo.gl/6gUzPA}{ TerrasMap }, \href{https://goo.gl/eYX5SW}{ MapBiomas }, \href{https://goo.gl/2J41hR}{SAD Plus} and \href{https://goo.gl/fCCp9s}{CarMap}. I acquire a large experience working with Python on web pages, manipulating tasks, numeric calculations and geospatial processing. Since 2014 I am an active and passionate member of the Brazilian \href{http://pynorte.python.org.br}{PyNorte} community and attended the national conferences in 2016, 2015 and 2014. Besides that I participate regularly in hangouts and I am conducting Coding Dojo sections as a tutor. In 2015 I founded with five friends the community PyNorte  from the Amazon region of Brazil with already more than 130 participants. Currently we are organizing the first regional \href{http://amazonia.python.org.br/}{PyCon Amazônia} conference which will take place in Manaus in August this year.

As backend development experiences I can highlight the personal \href{https://goo.gl/wrN029}{web page} that I created with Django and project geo using Pandas to handle csv, xlsx and xls files. Additionally I possess a large knowledge of full-stack architectures that I developed through work experiences and personal studies with Javascript frameworks like NodeJS, AngularJS, Backbone.js, Jasmine, JQuery, React and Redux. My focus on manipulating large spatial data volumes in PostgreSQL/PostGIS databases makes SQL and Relational powerful tools in my hands. Furthermore I applied Java successfully in developing the above mentioned Android applications where I used object-oriented programming (OOP), design patterns and architectures like MVC, Present First and Domain Driven Development. I have experience working with cloud services and deployment of applications, using AWS services like Amazon S3 and Amazon EC2. I dispose a balanced analytical mindset which allows me not to put blind faith in extensively analysed data and neither invalidate data on its first acquisition. Furthermore I am constantly researching new plugins for Java and Python libraries and include them successfully in my projects. Consequently I have an excellent judgement on deciding which one is the better choice for a specific goal in order to create and refine web systems.

As my experiences illustrate I am particularly well-qualified for the position and besides my experiences I am also thrilled to learn new skills and methods to find the best solution for any problem. In doing so I do not spare any effort or time to find potential weak spots and investigate new approaches to improve the tools I build. I thrive in an atmosphere of challenge, I am a quick learner and team player with a positive attitude and energy. My desire in expanding my professional horizons combined with a position such as this one in a city that offers an alternative lifestyle and good public transportation system seems like a match to me. I believe that I can very comfortably meet your requirements as the ideal candidate for this position and enthusiastically anticipate discussing your specific needs and my ability to meet them in an interview.

\closing{Thank you very much in advance for your consideration. I look forward to speaking with you next week.}
\vspace{10pt}
\ps

P.S. If you would like to get in touch more quickly and learn how I used Django and Flask Python web frameworks together with AngularJS and Backbone.js to create web map applications like TerrasMap, MapBiomas and the SAD Plus for my current employer, call me on my cell phone as soon as you read this: + 55 91 98220-3284.
\vspace{\fill}
\encl{Resume}

\end{letter}
\end{document}
