\documentclass[a4paper]{joaosoares-letter}
\usepackage{ragged2e}
\signature{João Soares}

\begin{document}
\longindentation=0pt


\begin{letter}{\bfseries HERE\\Invalidenstraße 116\\10115 Berlin\\Germany}

\namesection{João}{Soares}{	Passagem Liberal 245, Belém, PA, Brazil \ \lpipe\ \ eng.jmsoares@gmail.com \ \lpipe\ \ + 55 91 98220-3284}

\date{Belém, \today}


\opening{Dear Ms. Sharma,}{(Sr.) Software Test Engineer - Berlin, Germany on LinkedIn (18.02.2017)}

I am excited to learn of your job opening because I have been searching for a company just like yours to challenge my programming skills and improve my personal strengths in a motivated and highly functional team. In reviewing my resume, you will find that I possess all the attributes of a perfect match, from programming skills mainly in Java, Python and C to developing, maintaining and improving strong and stable mapping tools for web services (\href{https://goo.gl/6gUzPA}{ TerrasMap }, \href{https://goo.gl/eYX5SW}{ MapBiomas }, \href{https://goo.gl/2J41hR}{ SAD Plus }, \href{https://goo.gl/fCCp9s}{ CarMap }) and Android (\href{https://goo.gl/RcdbHk}{ Monitoramento de Pragas }, \href{https://goo.gl/OyZXke}{ Terras Monitoramento }, \href{https://goo.gl/mycBmL}{ Agrogestor }).

During my four years of experience as a Full-stack Software Developer I have gained major experiences in test automation frameworks, like PyUnit, Jasmine, JUnit, Robotium and PHPUnit that I implemented successfully in the above mentioned products. Additionally I have a broad and object oriented expertise of Java and C as well as professional experience working with Python, Javascript and Java for Android. To guarantee the success of an application I combine tools like git, Jenkins and Cucumber and integrate them into Android projects. I acquire great experiences in software development working in proactive teams where the elimination of errors has the highest priority. This can be accomplished by keeping the test environment as close to the real scenario as possible and I like to encourage and share these practices in my software developing team. Due to my programming skills combined with my personal studies and the fact that I include continuously new technologies into my projects I have an excellent judgement on deciding which tool is the best choice in order to write, develop, maintain and execute test cases.

One of my major projects was the MapBiomas project, a cooperation between international and Brazilian institutions for visualizing annual land use. In preparation for this project I participated in the Google Earth Engine User Summit in California where I attended the initial meeting of MapBiomas. Throughout the whole cooperation I worked in an international team where my major responsibilities were the front-end development of the MapBiomas workspace.

as a member of the Brazilian Python community I am searching for a company just like yours to challenge my programming skills and improve my personal strengths in a motivated and highly functional team. In reviewing my resume, you will find that I possess all the attributes of a perfect match, from programming skills mainly in Python, Javascript and Java to frameworks like Django and Node.js.


As my experiences illustrate I am particularly well-qualified for the position. I am also thrilled to learn new skills and methods and improve my personal strengths in a motivated and highly functional team. In doing so I do not spare any effort or time to find potential weak spots and investigate new approaches to improve the user experience. As a team player with a positive attitude and energy I love to discuss possible options with my colleagues to identify reasons and specify goals with the aim of finding the best solution together. I thrive in an atmosphere of challenge, I am a quick learner and my ability to apply new technologies and skills will boost the gain of HERE.

As backend development experiences I can highlight the personal \href{https://goo.gl/wrN029}{web page} that I created with Django and project geo using Pandas to handle csv, xlsx and xls files. Additionally I possess a large knowledge of full-stack architectures that I developed through work experiences and personal studies with Javascript frameworks like NodeJS, AngularJS, Backbone.js, Jasmine, JQuery, React and Redux. My focus on manipulating large spatial data volumes in PostgreSQL/PostGIS databases makes SQL and Relational powerful tools in my hands. Furthermore I applied Java successfully in developing the above mentioned Android applications where I used object-oriented programming (OOP), design patterns and architectures like MVC, Present First and Domain Driven Development. I have experience working with cloud services and deployment of applications, using AWS services like Amazon S3 and Amazon EC2. I dispose a balanced analytical mindset which allows me not to put blind faith in extensively analysed data and neither invalidate data on its first acquisition. Furthermore I am constantly researching new plugins for Java and Python libraries and include them successfully in my projects. Consequently I have an excellent judgement on deciding which one is the better choice for a specific goal in order to create and refine web systems.

As my experiences illustrate I am particularly well-qualified for the position and besides my experiences I am also thrilled to learn new skills and methods to find the best solution for any problem. In doing so I do not spare any effort or time to find potential weak spots and investigate new approaches to improve the tools I build. I thrive in an atmosphere of challenge, I am a quick learner and team player with a positive attitude and energy. My desire in expanding my professional horizons combined with a position such as this one in a city that offers an alternative lifestyle and good public transportation system seems like a match to me. I believe that I can very comfortably meet your requirements as the ideal candidate for this position and enthusiastically anticipate discussing your specific needs and my ability to meet them in an interview.

\closing{Thank you very much in advance for your consideration. I look forward to speaking with you next week.}
\vspace{10pt}
\ps

P.S. If you would like to get in touch more quickly and learn more about how I included test automation frameworks in different projects like TerrasMap, MapBiomas and Monitoramento de Pragas, call me on my cell phone as soon as you read this: + 55 91 98220-3284.
\vspace{\fill}
\encl{Resume}

\end{letter}
\end{document}
