\documentclass[a4paper]{joaosoares-letter}
\usepackage{ragged2e}
\signature{João Soares}

\begin{document}
\longindentation=0pt


\begin{letter}{\bfseries Ocono Tech GmbH\\Schwedter Str. 263\\10119 Berlin\\Germany}

\namesection{João}{Soares}{	Passagem Liberal 245, Belém, PA, Brazil \ \lpipe\ \ eng.jmsoares@gmail.com \ \lpipe\ \ + 55 91 98220-3284}

\date{Belém, \today}


\opening{Good morning,}{Backend Engineer (Python) - Berlin, Germany on Berlin Start Up Jobs (05.03.2017)}

I am excited to learn of your job opening because I have been searching for a company just like yours to challenge my programming skills and improve my personal strengths in a motivated and highly functional team. In reviewing my resume, you will find that I possess all the attributes of a perfect match, from programming skills in Python, SQL, Git, testing and Amazon Web Services to developing, maintaining and improving strong and stable mapping tools for web services and Android.

During my four years of experience as a Full-stack Software Developer I have gained major knowledge of backend architectures that I developed through work experiences in proactive international teams and personal studies. As a team player with a positive attitude and energy I love to discuss possible options with my colleagues as well as encourage and share new practices in my software developing team with the aim of finding the best solution together. Through these practices, I acquire an excellent judgement on deciding which tool is the best choice for a specific goal in order to create and refine sustainable and responsive web systems.

Since 2014 I am an active and passionate member of the \href{http://python.org.br}{Brazilian Python community} and attended the national conferences in 2016, 2015 and 2014. Additionally, I participate regularly in hangouts and I am conducting Coding Dojo sections as a tutor. In 2015 I founded with five friends the community \href{http://pynorte.python.org.br}{PyNorte} from the Amazon region of Brazil with already more than 130 participants. Currently we are organizing the first regional \href{http://amazonia.python.org.br/}{PyCon Amazônia} conference which will take place in Manaus in August this year.

As my experiences illustrate I am particularly well-qualified for the position. I am a Brazilian citizen currently living in Belém, and am planning to relocate to Berlin. I thrive in an atmosphere of challenge, I am a quick learner and I do not spare any effort or time to find potential weak spots which will boost the gain of Ocono.

I believe that I can very comfortably meet your requirements as the ideal candidate for this position and enthusiastically anticipate discussing your specific needs and my ability to meet them in an interview.

\closing{Thank you very much in advance for your consideration. I look forward to speaking with you next week.}
\vspace{10pt}
\ps

P.S. If you would like to get in touch more quickly and learn how I used Python in agile teams and put knowledge into practice such as DDD, TDD and Scrum in order to create strong web applications like \href{https://goo.gl/6gUzPA}{TerrasMap}, \href{https://goo.gl/eYX5SW}{MapBiomas} and \href{https://goo.gl/2J41hR}{SAD Plus} for my current employer, call me on my cell phone as soon as you read this: + 55 91 98220-3284.
\vspace{\fill}
\encl{Resume}

\end{letter}
\end{document}
