\documentclass[a4paper]{joaosoares-letter}
\usepackage{ragged2e}
\signature{João Soares}

\begin{document}
\longindentation=0pt


\begin{letter}{\bfseries Liquid Democracy e.V\\Am Sudhaus 2\\12053 Berlin\\Germany}

\namesection{João}{Soares}{	Passagem Liberal 245, Belém, PA, Brazil \ \lpipe\ \ eng.jmsoares@gmail.com \ \lpipe\ \ + 55 91 98220-3284}

\date{Belém, \today}


\opening{Dear Ms. Noffke,}{Django Developer - Berlin, Germany on your web page (21.02.2017)}

as a member of the Brazilian Python community I am searching for a company just like yours to challenge my programming skills and improve my personal strengths in a motivated and highly functional team. In reviewing my resume, you will find that I possess all the attributes of a perfect match, from programming skills in Python, Javascript and SCSS to developing, maintaining and improving strong and stable mapping tools for web services and Android surrounding web mapping applications, REST API services and open public data.

My four years of experience as a Full-stack Software Developer at the NGO \href{http://imazon.org.br/?lang=en}{IMAZON} and the Start Up \href{http://terras.agr.br/}{TERRAS} that was founded in IMAZON put me face to face with concerning environmental problems such as the Amazon deforestation and its contributions to the growth in global $CO_2$ emissions. During this time I have gained major knowledge of frontend and backend architectures that I developed through work experiences in proactive international teams and personal studies. As a team player with a positive attitude and energy I love to discuss possible options with my colleagues as well as encourage and share new practices in my software developing team with the aim of finding the best solution together. Through these practices, I acquire an excellent judgement on deciding which tool is the best choice for a specific goal in order to create and refine sustainable and responsive web systems.

Since 2014 I am an active and passionate member of the \href{http://python.org.br}{Brazilian Python community} and attended the national conferences in 2016, 2015 and 2014. Additionally, I participate regularly in hangouts and I am conducting Coding Dojo sections as a tutor. In 2015 I founded with five friends the community \href{http://pynorte.python.org.br}{PyNorte} from the Amazon region of Brazil with already more than 130 participants. Currently we are organizing the first regional \href{http://amazonia.python.org.br/}{PyCon Amazônia} conference which will take place in Manaus in August this year.

As my experiences illustrate I am particularly well-qualified for the position. I am a Brazilian citizen currently living in Belém, and am planning to relocate to Berlin. I thrive in an atmosphere of challenge, I am a quick learner and I do not spare any effort or time to find potential weak spots which will boost the gain of Liquid Democracy.

\closing{Thank you very much in advance for your consideration. I look forward to speaking with you.}
\vspace{10pt}
\ps


P.S. If you would like to get in touch more quickly and learn how I used Django and Flask Python web frameworks together with AngularJS and Backbone.js to create web map applications like \href{https://goo.gl/6gUzPA}{TerrasMap}, \href{https://goo.gl/eYX5SW}{MapBiomas} and \href{https://goo.gl/2J41hR}{SAD Plus} for my current employer, call me on my cell phone as soon as you read this: + 55 91 98220-3284.
\vspace{\fill}
\encl{Resume}

\end{letter}
\end{document}
